Background for transient faults in asynchronous circuits

### 2019-04-15 draft_together3.tex
Updates from Overleaf

\chapter{Fault Tolerant Circuit Under Normal Operation and Single Transient Fault}
\section{Traces and circuit equivalence}
We solve the problem of SEUs by taking a semi-modular circuit (the original circuit) and applying a transformation to the circuit by duplicating all its circuit elements.  Due to the asynchronous nature of how signals are processed, the resulting half circuits may have signals of corresponding wires at different values.  To solve this problem we add C-elements to synchronize the two versions of the same signal.  In the rest of this chapter we define a way to compare two circuits and to show their equivalence.  Then we propose our transformation method and show that under normal operation (no faults), the fault tolerant circuit is equivalent to the original.  Finally we show that if an SEU occurs, one side of the fault tolerant circuit is equivalent to the original and we can still extract the signals that we desire.\\

Other than the basic terminology for asynchronous circuits and state graphs, we also want terminology to compare two circuits and especially evaluate whether they implement the same state graph.  
We first define a trace, to describe the different paths a circuit can take as it follows the state graph.  Different paths can occur because each state may have multiple transitions from that state.  We record the succession of states and transitions by the trace which is defined as follows:
\begin{definition}A {\em trace} $\sigma$ of a circuit is a sequence of states of infinite length where $s_i$ is the $i^{th}$ term of the sequence.  Formally this is written as $\sigma: \mathbb{N} \to S$ and $T(s_i,s_{i+1})$ for $\forall i \in \mathbb{N}$.  We also use the $\sigma_n$ as shorthand to denote the sequence of the first n states of $\sigma$$\end{definition} 
Our definition of trace includes the case where there is only one transition from each state of a state graph, that is a linear state graph.  \\
%add finite traces
% all states or just the state graph ones

>>>>

\chapter{Fault Tolerant Circuit Under Normal Operation and Single Transient Fault}
\section{Traces and circuit equivalence}
We solve the problem of single transient faults by taking a semi-modular circuit (the original circuit) and applying a transformation to the circuit by duplicating all its circuit elements.  Due to the asynchronous nature of how signals are processed, the resulting half circuits may have signals of corresponding wires at different values.  To solve this problem we add C-elements to synchronize the two versions of the same signal.  In the rest of this chapter we define a way to compare two circuits and to show their equivalence.  Then we propose our transformation method and show that under normal operation (no faults), the fault tolerant circuit is equivalent to the original.  Finally we show that if a single transient fault occurs, one side of the fault tolerant circuit is equivalent to the original and we can still extract the signals that we desire.\\

Other than the basic terminology for asynchronous circuits and state graphs, we also want terminology to compare two circuits and especially to evaluate whether they implement the same state graph.  
We first define a trace, to describe the different paths a circuit can take as it follows the state graph.  Different paths can occur because there may be multiple transitions from each state.  We call the succession of states and transitions the trace which is defined as follows:
\begin{definition}A {\em trace} $\sigma$ of a circuit is a sequence of states of infinite length where $s_i$ is the $i^{th}$ term of the sequence.  Formally this is written as $\sigma: \mathbb{N} \to S$ and $T(s_i,s_{i+1})$ for $\forall i \in \mathbb{N}$.  We also use the $\sigma_n$ as shorthand to denote the sequence of the first n states of $\sigma$\end{definition} 
Our definition of trace includes the case where there is only one transition from each state of a state graph, that is a linear state graph.  \\
%add finite traces
% all states or just the state graph ones
